%-------------------------
% Resume in LaTeX — Govind Mishra
% Based on Jake's Resume Template
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx} 
\usepackage{fontawesome5}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Govind Mishra} \\ \vspace{1pt}
    \small
    \faGithub\ \href{https://github.com/Govind933}{\underline{Govind933}} $|$
    \faLinkedin\ \href{https://linkedin.com/in/Govind}{\underline{Govind}} $|$
    \faEnvelope\ \href{mailto:govindmishra933705@gmail.com}{\underline{govindmishra933705@gmail.com}} $|$
    \faPhone\ +91-8882471667
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
Backend Software Engineer with 1+ year of experience specializing in NestJS, Spring Boot, and PostgreSQL. Proven track record of building enterprise-grade Lead Management Systems (LMS) from scratch, handling 10M+ data rows, and improving database performance by 60\%. Experienced in high-throughput architectures, microservices, and secure API development.

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University School of Information, Communication \& Technology (USICT)}{July 2020 -- July 2024}
      {Bachelor of Technology in Computer Science and Engineering}{GPA: 8.08/10.0}
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript, Java, JavaScript, C++, SQL, PHP, HTML/CSS} \\
     \textbf{Backend}{: NestJS, Spring Boot, Node.js, Express, REST APIs, Microservices, Socket.io} \\
     \textbf{Databases}{: PostgreSQL (Materialized Views, CTEs, JSONB), MongoDB, Redis, MySQL, TypeORM} \\
     \textbf{Tools/Cloud}{: BullMQ, AWS (S3, SES), Firebase, Docker, Git, JWT, RBAC, Redux Toolkit}
    }}
 \end{itemize}

%-----------PROFESSIONAL EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer (Backend)}{Feb 2025 -- Present}
      {KollegeApply}{Gurgaon, India}
      \resumeItemListStart
        \resumeItem{\textbf{Lead Management System (Product built from scratch):} Designed and developed an enterprise LMS using NestJS and TypeScript, supporting high-throughput ingestion of 1,000+ leads/minute with multi-tenant campaigns and secure JWT/API-key authentication.}
        \resumeItem{\textbf{Scale \& Data Optimization:} Designed a PostgreSQL Materialized View strategy over 10M+ delivery logs with concurrent refresh and hybrid historical/near-real-time exclusion, enabling sub-second lead filtering.}
        \resumeItem{\textbf{High-Throughput Pipeline:} Built a non-blocking delivery pipeline using BullMQ, Redis, and Lua scripts for atomic pop-and-mark operations, enforcing API rate limits and concurrency across distributed workers.}
        \resumeItem{\textbf{Compliance \& Communication:} Implemented RBAC, dual approvals, and GDPR-compliant JSONB audit logging; developed SMS/Email modules with DLT templates, scheduling, URL shortening, and pixel-based click/open tracking.}
        \resumeItem{\textbf{KollegeApply Website \& CMS:} Scaled backend services to support 100,000+ monthly visitors; optimized complex college/exam filtering and improved critical API response times by 60\%.}
        \resumeItem{\textbf{Modular CMS Architecture:} Architected a modular CMS (25+ modules) enabling non-technical teams to manage content, bulk uploads, URL redirections, and faceted search with full auditability.}
      \resumeItemListEnd

    \resumeSubheading
      {Technical Tutor / Code Mentor}{Feb 2024 -- Jan 2025}
      {Trivium (Tutor.com)}{Remote}
      \resumeItemListStart
        \resumeItem{Delivered advanced, chat-based technical mentoring supporting students in C++ and Java with a strong focus on Data Structures \& Algorithms (DSA) and backend fundamentals.}
        \resumeItem{Diagnosed and resolved complex logical, runtime, and performance issues in student code, simulating real-world debugging workflows used in production engineering teams.}
        \resumeItem{Strengthened learners' problem-solving, algorithmic thinking, and code optimization skills by breaking down large problems into executable steps rather than providing direct solutions.}
        \resumeItem{Regularly worked with unstructured or incomplete problem statements, translating requirements into clear, testable logic — mirroring backend requirement analysis.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------TECHNICAL PROJECTS-----------
\section{Technical Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Video Sharing Platform} $|$ \emph{Spring Boot, React, MongoDB, Firebase}}{Jan 2024 -- Apr 2024}
      \resumeItemListStart
        \resumeItem{Built a full-stack video platform with a custom video player; integrated Firebase Storage for large media handling.}
        \resumeItem{Implemented backend validation, DTO mapping, and global exception handling for robust APIs.}
        \resumeItem{Optimized MongoDB queries and frontend state using Redux Toolkit, reducing load times by 40\%.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Software Development Cell (SDC), USICT}}{Nov 2021 -- Nov 2023}
      \resumeItemListStart
        \resumeItem{Led backend revamp of the university website using PHP and MySQL, supporting 114+ colleges.}
        \resumeItem{Built a student feedback portal using Angular and MySQL for 5,000+ users.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------
\section{Achievements}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{1st Place, KollegeApply Internal Hackathon}}{}
      \resumeItemListStart
        \resumeItem{Built an AI-powered college recommendation system using NestJS and vector embeddings, evaluated across scalability, accuracy, and real-world applicability.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

  

%-------------------------------------------
\end{document}
